Staged Abstract Interpreters

### 2019-04-06 paper/60_cases.tex
paper

In this section, we show that \citeauthor{Boucher:1996:ACN:647473.727587}'s AC
(closure generation as example) can be understood and implemented as an instance
of staging abstract interpreters. We first revisit the original implementation
of abstract compilation of 0-CFA, and then reproduce their result by simply
adding stage annotations.
The generated program of our approach improves approximately the same extent of
speed, but without changing a single line of the analyzer program using
type-based staging annotations. However, AC requires more engineering effort,
i.e., rewriting the whole analyzer into the closure generation form. Moreover,
as shown in Section~\ref{staged_ds}, our approach is able to not only remove the
interpretive overhead, but also enabling several optimizations such specialized
data structures and equivalent rewritings.

>>>>

In this section, we show that the AC (closure generation as example) can be
understood and implemented as an instance of staging abstract interpreters. We
first revisit the original implementation of abstract compilation of 0-CFA, and
then reproduce their result by simply adding stage annotations.
The generated program of our approach improves approximately the same extent of
speed, but without changing a single line of the analyzer program using
type-based staging annotations. However, AC requires more engineering effort,
i.e., rewriting the whole analyzer into the closure generation form. Moreover,
as shown in Section~\ref{staged_ds}, our approach is able to not only remove the
interpretive overhead, but also enabling several optimizations such specialized
data structures and equivalent rewritings.
